---
title: "RandomArt Package"
author: "Fleur Korzilius"
date: "28-1-2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("ggplot2")
library(ggplot2)
```

This is a demonstration of the Random Art package, that includes the make_art function. 
The function make_art allows you to create beautifully random art.
You can run make_art with an argument that sets the seed, to be able to recreate your beautiful art again.
However, you can also run it without any argument and enjoy the fleeting beauty.

## Form of the function
The function looks like this:

```{r make_art function, echo = TRUE, eval = TRUE}
make_art <- function(seed = NA) {
  if (!is.na(seed)) {
    set.seed(seed)
  }
  x <- sample(1000)
  y <- rnorm(100)
  df_art <- data.frame(x,y)

  art <- ggplot(df_art, aes(x, y)) +
    geom_point(aes(color = y))
  art + theme(axis.title = element_blank()) +
    theme(legend.position = "none",
          panel.background = element_blank(),
          axis.text = element_blank(),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_blank()) +
    stat_density_2d_filled(aes(fill = ..level..), geom="polygon")
}
```

## Trying the make_art function

First we will try the function without any arguments.

```{r, echo=TRUE, eval = TRUE}
make_art()
```

Now we will try the function by inputting different seeds.

```{r, echo = TRUE, eval = TRUE}
make_art(26)
make_art(17)
make_art(89)
make_art(1260)
```

This was a demonstration of the Random Art package for R. 
