---
title: "RandomArt Package"
author: "Fleur Korzilius"
date: "28-1-2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

This is a demonstration of the Random Art package, that includes the make_art function. 
The function make_art creates random art.
It allows you to run it with an argument that sets the seed, or you can run it without any argument.

## Form of the function
The function looks like this:

```{r make_art function, echo = TRUE, eval = TRUE}
make_art <- function(seed = NA) {
  if (!is.na(seed)) {
    set.seed(seed)
  }
  x <- sample(1000)
  y <- rnorm(100)
  df_art <- data.frame(x,y)

  art <- ggplot(df_art, aes(x, y)) +
    geom_point(aes(color = y))
  art + theme(axis.title = element_blank()) +
    theme(legend.position = "none",
          panel.background = element_blank(),
          axis.text = element_blank(),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_blank()) +
    stat_density_2d_filled(aes(fill = ..level..), geom="polygon")
}
```

## Trying the make_art function

First we will try the function without any arguments.

```{r, echo=TRUE, eval = TRUE}
make_art()
```

Now we will try the function by inputting different seeds.

```{r, echo = TRUE, eval = TRUE}
make_art(26)
make_art(17)
make_art(89)
make_art(1260)
```

This was a demonstration of the Random Art package for R. 